% Corder_Guy_Resume.tex

\documentclass[10pt,letterpaper]{article}

\usepackage[
    ignoreheadfoot,
    top=0.5in,
    bottom=0.5in,
    left=0.75in,
    right=0.75in,
    footskip=0in,
]{geometry}
\usepackage{titlesec}
\usepackage{tabularx}
\usepackage{array}
\usepackage[dvipsnames]{xcolor}
\usepackage{enumitem}
\usepackage{fontawesome5}
\usepackage{amsmath}
\usepackage[
    pdftitle={Corder Guy's Resume},
    pdfauthor={Corder Guy},
    pdfcreator={LaTeX with RenderCV},
    colorlinks=true,
    urlcolor=primaryColor
]{hyperref}
\usepackage[pscoord]{eso-pic}
\usepackage{calc}
\usepackage{bookmark}
\usepackage{lastpage}
\usepackage{changepage}
\usepackage{paracol}
\usepackage{ifthen}
\usepackage{needspace}
\usepackage{iftex}
\usepackage{charter}

\definecolor{primaryColor}{RGB}{0, 0, 0}

\ifPDFTeX
  \input{glyphtounicode}
  \pdfgentounicode=1
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{lmodern}
\fi

\raggedright
\AtBeginEnvironment{adjustwidth}{\partopsep0pt}
\pagestyle{empty}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}
\setlength{\topskip}{0pt}
\setlength{\columnsep}{0.15cm}
\pagenumbering{gobble}

\titleformat{\section}{
  \needspace{4\baselineskip}
  \bfseries
  \large
}{}{
  0pt
}{}[
  \vspace{1pt}
  \titlerule
]

\titlespacing{\section}{-1pt}{0.3cm}{0.2cm}

\newenvironment{header}{
    \setlength{\topsep}{0pt}
    \par
    \kern
    \topsep
    \centering
    \linespread{1.5}
  }{
    \par
    \kern
    \topsep
  }

\newenvironment{onecolentry}{
    \begin{adjustwidth}{0cm}{0cm}
  }{
    \end{adjustwidth}
  }

\newenvironment{twocolentry}[2][]{
    \onecolentry
    \def\secondColumn{#2}
    \setcolumnwidth{\fill, 4.5 cm}
    \begin{paracol}{2}
  }{
    \switchcolumn \raggedleft \secondColumn
    \end{paracol}
    \endonecolentry
  }

\renewcommand{\labelitemi}{\faIcon{arrow-right}}
\renewcommand{\labelitemii}{$\bullet$}
\newenvironment{highlights}{
  \setlist[itemize,1]{leftmargin=20pt}
  \setlist[itemize,2]{leftmargin=30pt}
  \begin{itemize}[
      topsep=0em,
      parsep=0.25em,
      partopsep=0em,
      itemsep=0pt
    ]
  }{
    \end{itemize}
  }

\begin{document}
  \newcommand{\AND}{\unskip
    \cleaders\copy\ANDbox\hskip\wd\ANDbox
    \ignorespaces
  }
  \newsavebox\ANDbox
  \sbox\ANDbox{$|$}

  \begin{header}
    \fontsize{25pt}{25pt}\selectfont Corder Guy

    \normalsize
    \mbox{Houston, TX, USA}
    \kern 5pt \AND \kern 5pt
    \mbox{\href{mailto:corder.guy@gmail.com}{corder.guy@gmail.com}}
    \kern 5pt \AND \kern 5pt
    \mbox{\href{tel:+1-512-994-8895}{512 994 8895}}
    \kern 5pt \AND \kern 5pt
    \mbox{\href{https://corder.tech/}{corder.tech}}
  \end{header}

  \vspace{5pt}

  \section{Relevant Work Experience}
  \setcolumnwidth{\fill, 5 cm}
  \begin{paracol}{2}
    \textbf{Software Engineer}, Two Sigma -- Houston, TX
    \switchcolumn
    \begin{flushright}
      August 2019 -- November 2024
    \end{flushright}
  \end{paracol}

  \vspace{-0.25cm}

  \begin{onecolentry}
    \begin{highlights}
      \item \textbf{\emph{Technical Lead -- OnCall Service}}
      \\ Led development of a translation layer integrating a vendor alerting product with internal infrastructure. Designed and maintained a high-reliability REST API with complex caching, Slack integration, error handling, and robust scalability.

        \begin{highlights}
          \item Transformed and scaled an intern-led project into a key component of multiple critical systems with \textbf{over 200 internal users.} Resolved technical issues while delivering \textbf{exceptional user support}.
          \item Engineered and maintained the backend in Java using Dropwizard and Google Guava, supported by \textbf{extensive integration testing} within our Jenkins CI/CD pipeline.
          \item Earned consistently \textbf{above-average performance} bonuses for technical excellence, impactful contributions, and \textbf{exceptional user support.}
        \end{highlights}

      \item \textbf{\emph{Selected Contributor -- Top-Priority Cross-Team Initiative}}
        \\ Hand-picked for a high-visibility task force, restructuring release path controls to ensure accountability and compliance.

        \begin{highlights}
          \item \textbf{Led integration with legacy workflows,} collaborating across \textbf{four teams} to gather requirements and implement seamless automation.
          \item Designed, implemented, and deployed a \textbf{Jira-integrated microservice,} enforcing approval workflows for \textbf{production-critical} releases.
        \end{highlights}

      \item \textbf{\emph{Intern Manager and Mentor}}

      \begin{highlights}
        \item Selected \textbf{three times} to \textbf{mentor engineering interns,} providing \textbf{technical guidance and professional development.}
        \item Provided \textbf{code reviews} and technical resources, ensuring interns contributed \textbf{production-level} code to three products.
      \end{highlights}

      \item \textbf{\emph{Technical Interviewer}}
        \\ Conducted \textbf{50+ technical interviews} for internship and full-time candidates, assessing skills in \textbf{algorithms, data structures, and backend development.}

        \begin{highlights}
          \item Delivered \textbf{prompt and detailed candidate feedback,} helping improve hiring decisions and refine interview processes.
          \item Provided training and advice to new interviewers, ensuring consistency in evaluations.
        \end{highlights}

      \item \textbf{\emph{Individual Contributor -- Web Components}}
        \\ Volunteered for a \textbf{crossteam pilot} of Web Components technology and \textbf{re-engineered} two independently- \\developed UI screens into a unified component, reducing code duplication by \textbf{70\%} and \textbf{streamlining development workflows}.

      \item \textbf{\emph{Hacker Lab Instructor}}
        \\ Designed and taught \textbf{hands-on workshops} on amateur radio, soldering, and 3D printing for \textbf{20+ participants.}
    \end{highlights}
  \end{onecolentry}

  \section{Technical Experience and Expertise}
  \begin{onecolentry}
    \begin{tabular}{l l}
      \textbf{Languages} & Java, Python, TypeScript, HTML, CSS \\
      \textbf{Frameworks} & Angular, Dropwizard, Flask, Web Components \\
      \textbf{Tools} & Git, Jira, GitHub, GitLab \\
      \textbf{Technologies} & Unit Testing, CI/CD, REST APIs, Linux, Windows \\
    \end{tabular}
  \end{onecolentry}

  \section{Education}
  \setcolumnwidth{\fill, 5 cm}
  \begin{paracol}{2}
    \textbf{Texas A\&M University}
    \switchcolumn
    \begin{flushright}
      September 2014 -- May 2019
    \end{flushright}
  \end{paracol}

  \vspace{-0.3cm}

  \begin{onecolentry}
    \hspace{10pt} \textbf{\emph{Computer Science}}, Bachelor of Science \\
    \hspace{10pt} \textbf{\emph{Cybersecurity}}, Minor \\
    \hspace{10pt} \textbf{\emph{Mathematics}}, Minor \\
  \end{onecolentry}

\end{document}
